Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2021-03-19 NEUROC/manuscript-submission-version/sec5-insights.tex
增加干净的提交版本
Minor revision提交版本.

    \item \emph{Sampling techniques can significantly reduce the memory usage per batch, but its implementation is still inefficient}.
          %
          The sampling techniques are effective under small batch sizes for both training and inference.
          %
          The accuracy of the GNN models trained with the sampling techniques is close to the accuracy of full-batch training.
          %
          With proper batch sizes, the accuracy of the sample-based training can be close to the accuracy of the full-batch training.
          %
          However, the current implementation of the sampling techniques in PyG brings considerable overheads when the batch size is small.
          %
          Improving the efficiency of the sampling techniques is a potential optimization direction.
          %
          The small sampled subgraphs cannot make full use of the computing power of the GPU either.
          %
          How to improve the GPU utilization under small batch sizes is another problem to solve.
          One possible solution is to train multiple batches asynchronously on the same GPU and use the asynchronous stochastic gradient descent to speed up the converge.
\end{enumerate}

>>>>

    \item \emph{Sampling techniques can significantly reduce the memory usage per batch, but their implementation is still inefficient}.
          %
          The sampling techniques are effective under small batch sizes for both training and inference.
          %
          With proper batch sizes, the accuracy of the sample-based training can be close to the accuracy of the full-batch training.
          %
          However, the current implementation of the sampling techniques in PyG brings considerable overheads when the batch size is small.
          %
          Improving the efficiency of the sampling techniques is a potential optimization direction.
          %
          The small sampled subgraphs cannot make full use of the computing power of the GPU either.
          %
          How to improve the GPU utilization under small batch sizes is another problem to solve.
          %
          One possible solution is to train multiple batches asynchronously on the same GPU and use the asynchronous stochastic gradient descent to speed up the converge.
\end{enumerate}

### 2021-03-19 NEUROC/sec4-experiments.tex
更新了正文中的文字问题
更新了文字问题
Minor revision提交版本.

\begin{figure}[H]
   \centering
   \subfloat{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
   \caption{Memory expansion ratios of typical GNNs in Inference.}
   \label{fig:memory_usage_analysis}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.pdf}
    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset:\texttt{amp}.}
    \label{fig:exp_sampling_minibatch_degrees_distribution}
\end{figure}

@@

\begin{figure}[H]
   \centering
   \subfloat[Average degree]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
   \subfloat[Number of edges]{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}

>>>>

\begin{figure}[H]
   \centering
   \subfloat{\includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}}
   \caption{Memory expansion ratios of typical GNNs in inference.}
   \label{fig:memory_usage_analysis}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\columnwidth]{figs/experiments/exp_sampling_minibatch_degrees_distribution_amazon-photo.pdf}
    \caption{Vertex degree distribution of the sampled subgraph (relative batch size: 6\%) and the original graph. Dataset: \texttt{amp}.}
    \label{fig:exp_sampling_minibatch_degrees_distribution}
\end{figure}

@@

\begin{figure}[H]
   \centering
   \subfloat[Average degree]{\includegraphics[width=0.4\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_avg_degrees.pdf}}
   \subfloat[Number of edges]{\includegraphics[width=0.4\columnwidth]{figs/experiments/exp_inference_sampling_graph_info_inference_sampler_edges.pdf}}
